\vspace*{-8mm}\textbf{\textsc{Novelty Detection for Semantic Place Categorization}}

### 2011-06-25 thesis/conclusion.tex
Thanks Diogo for spotting that.

% Summary of developed work
This thesis studied the problem of detecting novel situations in case of which the robot
lacks sufficient knowledge to explain the sensory information. It did so in the area of 
semantic mapping on indoor spaces, and more precisely, for the problem of detecting the situtation when
none of the known room category models were able to correctly explain the sensed spatial properties.

@@

g

>>>>

% Summary of developed work
This thesis studied the problem of detecting novel situations in case of which the robot
lacks sufficient knowledge to explain the sensory information. It did so in the area of 
semantic mapping on indoor spaces, and more precisely, for the problem of detecting the situation when
none of the known room category models were able to correctly explain the sensed spatial properties.

@@
